Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1123 at $z$=0.654

### 2016-05-18 WRITEUP/ms.tex
typesetting

%--------------------------------------------------------------------------
%                          Observations details
%--------------------------------------------------------------------------
\section{Observations}
\subsection{PdBI \bco} % DONE
Observations of the \bco rotational line ($\nu_{\rm rest}$ = 230.5379938 GHz)
toward the \gl galaxy RXJ1131-1231 at $z_{\rm QSO}$ =
0.658 were carried out using IRAM \pdbi (PdBI; Program ID: S14BX001; PI: D.
Riechers). Two observing runs were carried out on 2014 December 06 and 2015
February 05 under good weather conditions in the C and D array configurations,
respectively. The 2 mm receivers were used to cover the redshifted \bco line
and the underlying continuum emission, employing a correlator setup providing
an effective bandwidth of 3.6 GHz and a spectral resolution of 10.0 MHz ($\sim$
21.5 \kms). This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
 time after discarding unusable visibility data.
The nearby quasars 1127$-$145 and 1124$-$186 were observed every 22 minutes
for pointing, secondary amplitude, and phase calibration and 1055$+$018 was
observed as bandpass calibrators for both tracks.
MWC349 and 3C279 were observed as the primary flux calibrator for C and D
array observations, respectively, yielding $\lesssim$15\% calibration accuracy.

The \ncode{GILDAS} package was used to reduce and analyze the visibility data
which are then imaged and deconvolved using the CLEAN algorithm with ``natural"
weighting. This yields a synthesized clean beam size of 4$\farcs$44 $\times$ 1\farcs95 (PA = 13\degr).
The final rms noise is $\sigma$ = 1.451 mJy \kms
beam\pmOne over 10 MHz (21.5 \kms). The continuum image at $\nu_{\rm cont}\sim$
139 GHz is created by averaging over all the line-free channels. This
yields an rms noise of 0.082 mJy beam$^{-1}$. % see README.md in 04Sep15

@@

% poor phase note
% /Users/admin/Research/RXJ1131/CARMA/imagingD23/checkQuality.csh
%
% calflux source=1127-189 in=$MIRCAT/FluxSource.cat device=/xs
% Flux of: 1127-189  14FEB04.50 at 227.0 GHz:  0.65 Jy; rms: 0.10 Jy
% Extrapolate to 215.673 GHz with spectral index = -0.986 --> 0.684 Jy
% MIRIAD from bootstrap: Median Flux @ 215.673 GHz:     0.710
Given that the phase calibrator used for the first track was faint and was
observed under poor weather conditions and that the phase calibrator used for
the second track was far from our target source, the phase calibration is
subpar, with an rms scatter $\sim$60\degr. We thus conservatively estimate
a calibration accuracy of $\sim$45\% based on the flux scale uncertainties,
gain variation over time, and the phase scatter on the calibrated data. We
therefore treat its line intensity with caution and refrain using it to derive other physical quantities.

@@

\begin{figure}[tbph]
\centering
\includegraphics[width=0.45\textwidth]{../Figures/SpecCO21_twinx.eps}
\caption{ Spectrum of \bco emission toward RXJ1131. The velocity scale
is with respect to $z$=0.6537, which is approximately the line center
considering the asymmetry is as a result of differential lensing.
A more detailed discussion of differential lensing effect is presented in
\Sect{differential} and the magnification factors for various kinematic
components are listed in \Tab{mag}.
 \label{fig:CO21spec}}
\end{figure}

% moment 0 map: CASA chan=125~159 <=> GILDAS 126-160 <=> python 125-160
% - sigma = 0.305 Jy km/s/Beam
%   - note that theoretical sigma is lower = 1.5 * sqrt(160-126+1) * 21.5 ~ 0.2 Jy km/s /beam, due to higher noise in some channels with emission
We construct the zeroth, first and second moment maps shown in \Fig{CO21mom}
using the $uv$-continuum subtracted data cube, over $\Delta v$$\sim$750 \kms.
The first and second moment maps are clipped at 3$\sigma$.
The peak flux density is 8.12 $\pm$ 0.30 Jy\,\kms\,beam\pmOne in the intensity-
integrated map. The deconvolved source size is estimated to be 5\farc1$\pm$0\farc72 $\times$ 3\farcs72$\pm$0\farcs66 and thus the emission is resolved over
$\sim$2.2 beams. While the lensed emission is not strictly distributed as 2D-
Gaussian, the fit recovers the line intensity enclosed within the emitting
region, we therefore take this as an estimate on the extent of the lensed
emission. On the other hand, if we assume the spatial distribution of
the lensed molecular gas emission is similar to that in the optical to \nir
wavelengths, the lensed emission would be more accurately described by an
annulus, including the partially complete ``Einstein Ring" and
the lensed knots (see \Fig{CO21mom)}.

\begin{figure}[!htbp]
\centering
\includegraphics[trim=0 5 0 15, clip, width=0.25\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}
\includegraphics[trim=0 5 0 15, clip, width=0.25\textwidth]{../Figures/F555W_REDBLUE.eps}
\includegraphics[width=0.5\textwidth]{../Figures/CO_highOmom_CLIP5sigma}
\caption{
An overlay of the velocity-integrated \bco emission on the HST V$-$band (F555W)
image. The contours start at 3$\sigma$ and increment at steps of
$\pm$3$\sigma$, where $\sigma$=0.3 mJy beam\pmOne. The cross denotes the
location of the foreground galaxy at $z$=0.295. {\it Right: } The contours
are color coded to represent the red and blue wings of the emission.
\label{fig:CO21mom}}
\end{figure}

The emission of the red component coincides with the Einstein Ring seen in the
optical image, with most of its apparent flux originating from the lensed arc
in the Southeast, whereas the blue component is predominately coming from
solely the lensed arc shown in \Fig{CO21mom}. To illustrate this, we show the
channel maps of 21.5\,\kms width and spatial spectra of 1\farcs5 resolution in
\Fig{chanmap} and \Fig{spatial}, respectively. The figures show that emission
is present to the West and peaks toward the lensing arc (black across in \Fig{
chanmap}) in the red wing, and shifts to the East with decreasing velocity (
blue wing). This indicates extended emission in the source plane, where
emission from different kinematic components is separated by different amounts
relative to the caustics. One consequence of such is the observed asymmetric
line profile. A detailed analysis on differential lensing of \bco is presented in \Sec{differential}.

\begin{figure*}[!htbp]
\centering
\includegraphics[width=0.9\textwidth]{../Figures/co_channel_maps.eps}
\caption{
Channel maps of \pdbi \bco toward RXJ1131 in 21.5\,\kms resolution. The
Black crosses indicate the position of the lensed knots (AGN emission,
which are components ABCD in C06). The central white-filled
star indicates the position of the foreground lensing galaxy (component G
in C06), as detected in the HST image. Contours start and increment at steps of
$\pm$3$\sigma$. The beam is denoted in the bottom right panel. \label{fig:chanmap}}
\end{figure*}

\begin{figure*}[!htbp]
\centering
\includegraphics[width=0.9\textwidth]{../Figures/spatialSpec_offsetShifted.eps}
\caption{
\bco spectrum as a function of position, binned by 3 pixels in each
direction (1\farcs5). The spectra map covers an extent of $\sim$10"$\times$10"
centering on the pixel that corresponds to the lensing galaxy. The velocity
and flux density scales are denoted in the top right panel.
BLAH: DR would want the pixel coordinates replaced by arcsec offset from
center. \label{fig:spatialSpec}}
\end{figure*}

@@

\susbsection{Origin of the \bco emission} \label{sec:origin} %DONE
Evidently, the CO emission is co-spatial with the lensed optical emission in
the background AGN host galaxy. The question is then whether the optically
faint companion also contributes to the CO flux and thus contains a
non-negligible amount of molecular gas.
Indeed, based on our lens model presented in \Sec{lensmodel}, we find it
highly likely that part of the CO emission originates from
the companion. We thus classify RXJ1131 as a ``wet-wet'' merger.
However, we cannot quantify this with a mass ratio given the
spatial resolution. This will be verified in future higher-resolution observations. In the subsequent sections, we will interpret RXJ1131
using this scenario (i.e. a ``wet-wet'' merger).

@@

\begin{figure}[!htbp]
\centering
\includegraphics[trim=0 5 0 15, clip, width=0.25\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}
\includegraphics[trim=0 5 0 15, clip, width=0.25\textwidth]{../Figures/F555W_REDBLUE.eps}
\includegraphics[width=0.5\textwidth]{../Figures/CO_highOmom_CLIP5sigma}
\caption{
Contours for the first (left) and second (right) moment maps are shown in steps of 50 \kms, and 100 \kms, respectively. The beam (native resolution) is shown in the right panel.
\label{fig:CO21highO}}
\end{figure}

@@

\begin{figure}[!Htbp]
\centering
\includegraphics[width=0.5\textwidth]{../Figures/coOverlay.eps}
\caption{
\carma \cco line profile (solid) without continuum subtraction is
over-plotted on the continuum-subtracted \bco line profile (dashed).
The velocity scale is with respect to $z$=0.6537, which corresponds to the
dynamical center of the \bco line. The spectral resolution for \cco and \bco
is 35.8 \kms and 21.5 \kms, respectively.
 \label{fig:co32spec}}
\end{figure}

Assuming the spatial extents between \bco and \cco are similar and therefore
a negligible differential lensing effect, the line intensities
correspond to a brightness temperature ratio of
$r_{\rm 32}$\,=\,T$_{\tiny \cco}$/T$_{\tiny \bco}$\,=\,0.66$\pm$0.41.
The high uncertainty is dominated by the uncertainties in the \cco line
intensity.

@@

We detect PdBI 2\,mm continuum in \Fig{2mm}. The integrated flux density is
1.2$\pm$0.2 mJy, with a peak flux $S_\nu$ = 800$\pm$88 \micron Jy\,beam\pmOne
centering on the lensing galaxy. A slightly extended emission is also seen
along the lensed arc. This suggests that the detected emission comes from
both the foreground galaxy and the background galaxy and that the
emission is marginally resolved along its major axis.
We subtract a point source model in $uv$-plane to remove the unresolved
emission toward the foreground galaxy. The peak flux (0.389$\pm$0.082 mJy)
in the residual map coincides with the lensed arc, and is consistent with
the difference between the integrated and the peak flux in the
original continuum map ($\sim$0.4 mJy). We therefore adopt
$S_\nu$ = 0.39$\pm$0.08 mJy as the 2\,mm continuum emission toward
the background galaxy.

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.35\textwidth]{../Figures/F555W_ContPdBI.eps}
\caption{
An overlay of the 2\,mm continuum emission on the optical image. Contours start and increment at steps of $\pm$3$\sigma$, where $\sigma$\,=\,0.082 mJy
beam\pmOne. The central cross indicates the centroid of the foreground galaxy,
as detected in the optical image. The synthesis beam is shown in the bottom left corner.
\label{fig:2mm}}
\end{figure}

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.35\textwidth]{../Figures/F555W_ContVLA.eps}
\caption{
VLA 5\,GHz continuum emission is overlaid on the optical image. Contours start and increment at steps of $\pm$3$\sigma$ of $\sigma$=13\micron Jy beam\pmOne. The beam is shown in the bottom left corner.
 \label{fig:vla}}
\end{figure}

The VLA C-band continuum image in \Fig{vla} shows resolved emission from the
jets and core of the foreground elliptical galaxy
as well as emission toward the background quasar.
Multiple peaks are seen along the arc and their centroids
coincide with the optical emission from the quasar.
We extract the flux densities for the arc and the core in \Tab{photometry}.
We find a spectral index of $\alpha$\,=\,0.024 for the foreground
galaxy and $\alpha$\,=\,0.345 for the background galaxy by fitting a
power-law (S$_\nu \propto \nu^{-\alpha}$) to the continuum emission at
5\,GHz and 2\,mm.

@@

The emission in the IRAC images is slightly extended. We thus use the
HST image ($\sim$0\fracs07 resolution) to determine
origins of their centroids, all of which are found to be
centered at the position corresponding to the lensed emission from the
background galaxy. To recover the diffuse background emission, we subtract a
point source model centered on the lensing galaxy. We use the average
FWHM found by fitting a Gaussian profile to several field stars
using \ncode{imexam} routine of IRAF.
We perform aperture photometry on the residual image
to obtain decomposed flux measurements from the background galaxy.
The photometries for the foreground galaxy are then obtained
by subtracting the fluxes decomposed for the background source
from the observed total flux. The resulting photometry in
\Tab{photometry} are obtained after performing aperture correction
described in the IRAC Instrument Handbook\footnote{http://irsa.ipac.caltech.edu/data/SPITZER/docs/irac/iracinstrumenthandbook/} to
correct for the fact that the IRAC imaging was calibrated
using a 12" aperture, which is bigger than the aperture (5\farcs8) we used to
perform aperture photometry. This step was taken to provide
constraints on the Wien tail beyond the dust peak of the
spectral energy distribution (SED) of RXJ1131.
The details of the SED modeling is presented in \Sec{SED}.

@@

%--------------------------------------------------------------------------
%                                Analysis
%--------------------------------------------------------------------------
\section{Analysis}
\subsection{Lens modeling} \label{lensmodel}
The spectrally resolved lensed emission allows us to probe dynamical structures on smaller spatial scales than otherwise possible.

@@

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.85\textwidth]{../Figures/PostageStampModel.eps}
\includegraphics[width=0.85\textwidth]{../Figures/PostageStampResiduals.eps}
\caption{
Lens model of channel widths $\sim$ 100\kms.
Make this bigger in the future
Channel maps of the CO emission (red) overlaid on our best-fit lens models (grayscale). The foreground lensing galaxy is represented by a black dot. The reconstructed source morphology (magenta ellipses) is also suggestive of a “disk”.
\label{fig:model}}
\end{figure*}

@@

\subsection{\bco Dynamical modeling} \label{sec:dynamics}
Based on the the source plane position of each kinematic components from the
lens model, a clear symmetric velocity gradient is seen, which is suggestive of a rotating disk. Assuming the observed velocities of the respective channels
correspond to solely the tangential components (i.e. $\theta$ = 0), we extract
the major axis along the best-fit slice across these source plane positions,
which is along PA of 121\degr.
We attempt to characterize the molecular gas kinematics using an empirically motivated disk model (e.g. Courteau97, Peuch+08, Miller+11):
\begin{equation}
V = V_0 + \frac{2}{\pi} V_{\rm a} \arctan(\frac{R}{R_{\rm t}}),
\end{equation}
where $V$ is the observed velocity, $V_0$ is the velocity at dynamical center, $V_{\rm a}$ is the asymptotic velocity, and $R_{\rm t}$ is the ``turnover'' radius at which the rotation curve
becomes flat. We perform non-linear least square fitting using an orthogonal distance regression to find the best-fit $V_a$, $r_t$, $V_0$, taking into account
errors in both velocity and distance offset (see \Figure{PV}). We also place an upper limit on $r_t$ $<$ 15 kpc (Miller+11, Genzel+??, Puech+08?) to keep this
parameter physical. We then estimate the uncertainties associated with best-fit parameters using a Monte Carlo simulation of 500 iterations, perturbing
the velocity and physical separation according to a random Gaussian distribution of width/sigma based on the input uncertainties on
the data. Using this model, we find $V_a$ = 975$\pm$387, $r_t$ = 10.6$\pm$5.7,
and $V_0$ = 28$\pm$40. We note, however, that since emission is not detected beyond the flat regime of the rotation curve (Figure \ref{fig: PV}), the asymptotic velocity is
poorly constrained. In particular, $V_a$ and $r_t$ are highly correlated with a Pearson coefficient $r$ = 0.998 between the two, and 0.027 between $V_a$ and $V_0$.

@@

\subsection{SED modeling}

>>>>

%--------------------------------------------------------------------------
%                          Observations details
%--------------------------------------------------------------------------
\section{Observations}
\subsection{PdBI \bco} % DONE
Observations of the \bco rotational line ($\nu_{\rm rest}$ = 230.5379938 GHz)
toward the \gl galaxy RXJ1131-1231 at $z_{\rm QSO}$\,=\,0.658 
were carried out using IRAM \pdbi (PdBI; Program ID: S14BX001; PI: D.
Riechers). Two observing runs were carried out on 2014 December 06 and 2015
February 05 under good weather conditions in the C and D array configurations,
respectively. The 2 mm receivers were used to cover the redshifted \bco line
and the underlying continuum emission, employing a correlator setup providing
an effective bandwidth of 3.6 GHz and a spectral resolution of 10.0 MHz ($\sim$
21.5 \kms). This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
 time after discarding unusable visibility data.
The nearby quasars 1127$-$145 and 1124$-$186 were observed every 22 minutes
for pointing, secondary amplitude, and phase calibration and 1055$+$018 was
observed as bandpass calibrators for both tracks.
MWC349 and 3C279 were observed as the primary flux calibrator for C and D
array observations, respectively, yielding $\lesssim$15\% calibration accuracy.

The \ncode{GILDAS} package was used to reduce and analyze the visibility data
which are then imaged and deconvolved using the CLEAN algorithm with ``natural"
weighting. This yields a synthesized clean beam size of 4$\farcs$44 $\times$ 1\farcs95 (PA = 13\degr).
The final rms noise is $\sigma$ = 1.451 mJy \kms
beam\pmOne over 10 MHz (21.5 \kms). The continuum image at $\nu_{\rm cont}\sim$139\,GHz 
is created by averaging over all the line-free channels. This
yields an rms noise of 0.082 mJy beam$^{-1}$. % see README.md in 04Sep15

@@

% poor phase note
% /Users/admin/Research/RXJ1131/CARMA/imagingD23/checkQuality.csh
%
% calflux source=1127-189 in=$MIRCAT/FluxSource.cat device=/xs
% Flux of: 1127-189  14FEB04.50 at 227.0 GHz:  0.65 Jy; rms: 0.10 Jy
% Extrapolate to 215.673 GHz with spectral index = -0.986 --> 0.684 Jy
% MIRIAD from bootstrap: Median Flux @ 215.673 GHz:     0.710
Given that the phase calibrator used for the first track was faint and was
observed under poor weather conditions and that the phase calibrator used for
the second track was far from our target source, the phase calibration is
subpar, with an rms scatter $\sim$60\degr. We thus conservatively estimate
a calibration accuracy of $\sim$45\% based on the flux scale uncertainties,
gain variation over time, and the phase scatter on the calibrated data. We
therefore treat its line intensity with caution and refrain ourselves from 
using it to derive other physical quantities.

@@

\begin{figure}[tbph]
\centering
\includegraphics[width=0.45\textwidth]{../Figures/SpecCO21_twinx.eps}
\caption{ Spectrum of \bco emission toward RXJ1131. The velocity scale
is with respect to $z$=0.6537, which is approximately the line center
considering the asymmetry is as a result of differential lensing.
A more detailed discussion of differential lensing effect is presented in
\Sec{differential} and the magnification factors for various kinematic
components are listed in \Tab{mag}.
 \label{fig:CO21spec}}
\end{figure}

% moment 0 map: CASA chan=125~159 <=> GILDAS 126-160 <=> python 125-160
% - sigma = 0.305 Jy km/s/Beam
%   - note that theoretical sigma is lower = 1.5 * sqrt(160-126+1) * 21.5 ~ 0.2 Jy km/s /beam, due to higher noise in some channels with emission
We construct the zeroth, first and second moment maps shown in \Fig{CO21mom}
using the $uv$-continuum subtracted data cube, over $\Delta v$$\sim$750 \kms.
The first and second moment maps are clipped at 3$\sigma$.
The peak flux density is 8.12 $\pm$ 0.30 Jy\,\kms\,beam\pmOne in the intensity-integrated
map. The deconvolved source size is estimated to be 5\farcs1$\pm$0\farcs72 $\times$ 3\farcs72$\pm$0\farcs66 
and thus the emission is resolved over $\sim$2.2 beams. 
While the lensed emission is not strictly distributed as 2D-Gaussian, 
the fit recovers the line intensity enclosed within the emitting
region, we therefore take this as an estimate on the extent of the lensed
emission. On the other hand, if we assume the spatial distribution of
the lensed molecular gas emission is similar to that in the optical to \nir
wavelengths, the lensed emission would be more accurately described by an
annulus, including the partially complete ``Einstein Ring" and
the lensed knots (see \Fig{CO21mom}).

\begin{figure}[!htbp]
\centering
\includegraphics[trim=0 5 0 15, clip, width=0.232\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}
\includegraphics[trim=0 5 0 0, clip, width=0.22\textwidth]{../Figures/F555W_REDBLUE.eps}
\caption{
An overlay of the velocity-integrated \bco emission on the HST V$-$band (F555W)
image. The contours start at 3$\sigma$ and increment at steps of
$\pm$3$\sigma$, where $\sigma$\,=\,0.3 mJy beam\pmOne. The crosses denote the
location of the foreground galaxy at $z$\,=\,0.295. {\it Right:} The contours
are color-coded to represent the red and blue wings of the emission.
\label{fig:CO21mom}}
\end{figure}

The emission of the red component coincides with the Einstein Ring seen in the
optical image, with most of its apparent flux originating from the lensed arc
in the Southeast, whereas the blue component is predominately coming from
solely the lensed arc shown in \Fig{CO21mom}. To illustrate this, we show the
channel maps of 21.5\,\kms width and spatial spectra of 1\farcs5 resolution in
\Fig{chanmap} and \Fig{spatialSpec}, respectively. The figures show that emission
is present to the West and peaks toward the lensing arc (black across in \Fig{chanmap}) 
in the red wing, and shifts to the East with decreasing velocity (blue wing). 
This indicates extended emission in the source plane, where
emission from different kinematic components is separated by different amounts
relative to the caustics. One consequence of such is the observed asymmetric
line profile. A detailed analysis on differential lensing of \bco is presented in \Sec{differential}.

\begin{figure*}[tbph]
\centering
\includegraphics[width=1.0\textwidth]{../Figures/co_channel_maps.eps}
\caption{
Channel maps of \pdbi \bco toward RXJ1131 in 21.5\,\kms resolution. The
Black crosses indicate the position of the lensed knots (AGN emission,
which are components ABCD in C06). The central white-filled
star indicates the position of the foreground lensing galaxy (component G
in C06), as detected in the HST image. Contours start and increment at steps of
$\pm$3$\sigma$. The beam is denoted in the bottom right panel. \label{fig:chanmap}}
\end{figure*}

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.8\textwidth]{../Figures/spatialSpec_offsetShifted.eps}
\caption{
\bco spectrum as a function of position, binned by 3 pixels in each
direction (1\farcs5). The spectra map covers an extent of $\sim$10"$\times$10"
centering on the pixel that corresponds to the lensing galaxy. The velocity
and flux density scales are denoted in the top right panel.
BLAH: DR would want the pixel coordinates replaced by arcsec offset from
center. \label{fig:spatialSpec}}
\end{figure*}

@@

\subsection{Origin of the \bco emission} \label{sec:origin} %DONE
Evidently, the CO emission is co-spatial with the lensed optical emission in
the background AGN host galaxy. The question is then whether the optically
faint companion also contributes to the CO flux and thus contains a
non-negligible amount of molecular gas.
Indeed, based on our lens model presented in \Sec{lensmodel}, we find it
highly likely that part of the CO emission originates from
the companion. We thus classify RXJ1131 as a ``wet-wet'' merger.
However, we cannot quantify this with a mass ratio given the
spatial resolution. This will be verified in future higher-resolution observations. In the subsequent sections, we will interpret RXJ1131
using this scenario (i.e. a ``wet-wet'' merger).

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.45\textwidth]{../Figures/CO_highOmom_CLIP5sigma}
\caption{
Contours for the first (left) and second (right) moment maps are shown in steps of 
50 \kms, and 100 \kms, respectively. The beam (native resolution) is shown in the right panel.
\label{fig:CO21highO}}
\end{figure}

@@

\begin{figure}[!Htbp]
\centering
\includegraphics[width=0.455\textwidth]{../Figures/coOverlay.eps}
\caption{\carma \cco line profile (solid) without continuum subtraction is
over-plotted on the continuum-subtracted \bco line profile (dashed).
The velocity scale is with respect to $z$=0.6537, which corresponds to the
dynamical center of the \bco line. The spectral resolution for \cco and \bco
is 35.8 \kms and 21.5 \kms, respectively.
 \label{fig:co32spec}}
\end{figure}

Assuming the spatial extents between \bco and \cco are similar and therefore
a negligible differential lensing effect, the line intensities
correspond to a brightness temperature ratio of
$r_{\rm 32}$\,=\,T$_{\tiny \cco}$/T$_{\tiny \bco}$\,=\,0.66\,$\pm$\,0.41.
The high uncertainty is dominated by the uncertainties in the \cco line
intensity.

@@

We detect PdBI 2\,mm continuum in \Fig{cont}. The integrated flux density is
1.2$\pm$0.2 mJy, with a peak flux $S_\nu$ = 800$\pm$88 \micron Jy\,beam\pmOne
centering on the lensing galaxy. A slightly extended emission is also seen
along the lensed arc. This suggests that the detected emission comes from
both the foreground galaxy and the background galaxy and that the
emission is marginally resolved along its major axis.
We subtract a point source model in $uv$-plane to remove the unresolved
emission toward the foreground galaxy. The peak flux (0.389$\pm$0.082 mJy)
in the residual map coincides with the lensed arc, and is consistent with
the difference between the integrated and the peak flux in the
original continuum map ($\sim$0.4 mJy). We therefore adopt
$S_\nu$ = 0.39$\pm$0.08 mJy as the 2\,mm continuum emission toward
the background galaxy.

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.23\textwidth]{../Figures/F555W_ContPdBI.eps}
\hspace{-0.5em}
\includegraphics[width=0.235\textwidth]{../Figures/F555W_ContVLA.eps}
\caption{{\it Left:} An overlay of the 2\,mm continuum emission on the optical image. 
{\it Right:} VLA 5\,GHz continuum emission is overlaid on the optical image. 
Contours in both images start and increment at steps of 
$\pm$3$\sigma$, where $\sigma_{\rm 2mm}$\,=\,0.082 mJy beam\pmOne and 
$\sigma_{\rm 5GHz}$\,=\,13 $\mu$Jy beam\pmOne in the left and right panel, respectively.
The central crosses indicate the centroid of the foreground galaxy,
as detected in the optical image. The synthesis beams are shown in the bottom left corner of each panel.
\label{fig:cont}}\vspace{0.51em}
\end{figure}

The VLA C-band continuum image in \Fig{cont} shows resolved emission from the
jets and core of the foreground elliptical galaxy
as well as emission toward the background quasar.
Multiple peaks are seen along the arc and their centroids
coincide with the optical emission from the quasar.
We extract the flux densities for the arc and the core in \Tab{photometry}.
We find a spectral index of $\alpha$\,=\,0.024 for the foreground
galaxy and $\alpha$\,=\,0.345 for the background galaxy by fitting a
power-law (S$_\nu \propto \nu^{-\alpha}$) to the continuum emission at
5\,GHz and 2\,mm.

@@

The emission in the IRAC images is slightly extended. We thus use the
HST image ($\sim$0\farcs07 resolution) to determine
origins of their centroids, all of which are found to be
centered at the position corresponding to the lensed emission from the
background galaxy. To recover the diffuse background emission, we subtract a
point source model centered on the lensing galaxy. We use the average
FWHM found by fitting a Gaussian profile to several field stars
using \ncode{imexam} routine of IRAF.
We perform aperture photometry on the residual image
to obtain decomposed flux measurements from the background galaxy.
The photometries for the foreground galaxy are then obtained
by subtracting the fluxes decomposed for the background source
from the observed total flux. The resulting photometry in
\Tab{photometry} are obtained after performing aperture correction
described in the IRAC Instrument Handbook\footnote{http://irsa.ipac.caltech.edu/data/SPITZER/docs/irac/iracinstrumenthandbook/} to
correct for the fact that the IRAC imaging was calibrated
using a 12" aperture, which is bigger than the aperture (5\farcs8) we used to
perform aperture photometry. This step was taken to provide
constraints on the Wien tail beyond the dust peak of the
spectral energy distribution (SED) of RXJ1131.
The details of the SED modeling is presented in \Sec{SED}.

@@

%--------------------------------------------------------------------------
%                                Analysis
%--------------------------------------------------------------------------
\section{Analysis}
\subsection{Lens modeling} \label{sec:lensmodel}
The spectrally resolved lensed emission allows us to probe dynamical structures on smaller spatial scales than otherwise possible.

@@

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.85\textwidth]{../Figures/PostageStampModel.eps}
\includegraphics[width=0.85\textwidth]{../Figures/PostageStampResiduals.eps}
\caption{
Lens model of channel widths $\sim$ 100\kms.
Make this bigger in the future
Channel maps of the CO emission (red) overlaid on our best-fit lens models (grayscale). The foreground lensing galaxy is represented by a black dot. The reconstructed source morphology (magenta ellipses) is also suggestive of a disk.
\label{fig:model}}
\end{figure*}

@@

\subsection{\bco Dynamical modeling} \label{sec:dynamics}
Based on the the source plane position of each kinematic components from the
lens model, a clear symmetric velocity gradient is seen, which is suggestive of a rotating disk. Assuming the observed velocities of the respective channels
correspond to solely the tangential components (i.e. $\theta$ = 0), we extract
the major axis along the best-fit slice across these source plane positions,
which is along PA of 121\degr.
We attempt to characterize the molecular gas kinematics using an empirically motivated disk model (e.g. Courteau97, Peuch+08, Miller+11):
\begin{equation}
V = V_0 + \frac{2}{\pi} V_{\rm a} \arctan(\frac{R}{R_{\rm t}}),
\end{equation}
where $V$ is the observed velocity, $V_0$ is the velocity at dynamical center, $V_{\rm a}$ is the asymptotic velocity, and $R_{\rm t}$ is the ``turnover'' radius at which the rotation curve
becomes flat. We perform non-linear least square fitting using an orthogonal distance regression to find the best-fit $V_a$, $r_t$, $V_0$, taking into account
errors in both velocity and distance offset (see \Fig{PV}). We also place an upper limit on $r_t$ $<$ 15 kpc (Miller+11, Genzel+??, Puech+08?) to keep this
parameter physical. We then estimate the uncertainties associated with best-fit parameters using a Monte Carlo simulation of 500 iterations, perturbing
the velocity and physical separation according to a random Gaussian distribution of width/sigma based on the input uncertainties on
the data. Using this model, we find $V_a$ = 975$\pm$387, $r_t$ = 10.6$\pm$5.7,
and $V_0$ = 28$\pm$40. We note, however, that since emission is not detected beyond the flat regime of the rotation curve (Figure \ref{fig: PV}), the asymptotic velocity is
poorly constrained. In particular, $V_a$ and $r_t$ are highly correlated with a Pearson coefficient $r$ = 0.998 between the two, and 0.027 between $V_a$ and $V_0$.

@@

\subsection{SED modeling} \label{sec:SED}
